---
title: "stat630_project_group5"
author: "Group5"
date: "2022-12-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
# import data
olympic <- read_csv("winter_olympic_study.csv")
```

```{r}
dim(data)
head(olympic)
```

```{r}
sum(is.na(olympic))
```

### EDA

```{r}
summary(olympic)
```

```{r}
mean(olympic$Total_Points)
sd(olympic$Total_Points)
mean(olympic$GDP)
sd(olympic$GDP)
```

```{r}
hist(olympic$Total_Points)
```

```{r}
olympic %>%
  filter(year == 2018) %>% 
  select(country_name, Total_Points) %>% 
  arrange(desc(Total_Points)) %>%
  head(10)
```

```{r}
hist(olympic$GDP)
```

```{r}
olympic %>%
  filter(year == 2018) %>% 
  select(country_name, GDP) %>% 
  arrange(desc(GDP)) %>%
  head(10)
```

### Transformation

```{r}
olympic$loggdp <- log(olympic$GDP)
```

```{r}
plot(olympic$Total_Points ~ olympic$GDP)
plot(olympic$Total_Points ~ olympic$loggdp)
```

```{r}
mean(olympic$loggdp)
sd(olympic$loggdp)
```

### Analysis 1
### Check assumptions

#### 1. Linearity

```{r}
# 1. Linearity
ggplot(olympic, aes(x = log(GDP), y = Total_Points)) + 
  geom_point() +
  geom_smooth(method = "lm")
```

#### 2. Indepence

Each country is independent of one another.We assume that all the country's GDP and number of medals are independent.

#### 3. Equal Variance

```{r}
model1 <- lm(Total_Points ~ log(GDP), data = olympic)

plot(resid(model1) ~ fitted(model1), main = "Residuals vs. Fitted")  
abline(h = 0, col = "red")
```

#### 4. Normality

```{r}
qqnorm(resid(model1))
qqline(resid(model1), col = "red")
```

### Linear Regression
```{r}
model1
```

```{r}
summary(model1)
```

```{r}
confint(model1)
```

```{r}
ggplot(olympic, aes(x = log(GDP), y = Total_Points)) + 
  geom_point() +
    geom_smooth(method = "lm")+
  labs(x = "log(GDP)",
       y = "Total Medal Points",
       title = "Total Medal Points vs. log(GDP)")+
  theme_bw()
```

### Analysis 2
### Check assumptions

#### 1. Linearity

```{r}
# 1. Linearity
ggplot(olympic, aes(x = Atheletes, y = Total_Points)) + 
  geom_point() +
  geom_smooth(method = "lm")
```

#### 2. Indepence

Each country is independent of one another.We assume that all the number of Athletes and number of medals are independent.

#### 3. Equal Variance

```{r}
model2 <- lm(Total_Points ~ Atheletes, data = olympic)

plot(resid(model2) ~ fitted(model2), main = "Residuals vs. Fitted")  
abline(h = 0, col = "red")
```

#### 4. Normality

```{r}
qqnorm(resid(model2))
qqline(resid(model2), col = "red")
```

### Linear Regression
```{r}
model2
```

```{r}
summary(model2)
```

```{r}
confint(model2)
```

```{r}
ggplot(olympic, aes(x = Atheletes, y = Total_Points)) + 
  geom_point() +
    geom_smooth(method = "lm")+
  labs(x = "Atheletes",
       y = "Total Medal Points",
       title = "Total Medal Points vs. Atheletes")+
  theme_bw()
```
```{r}
olympic %>% 
  ggplot(aes(x = loggdp, y = Total_Points, col=Atheletes, size=Atheletes)) + 
  geom_point() +
  geom_smooth(method = "lm")
```

